### 2024-10-02 README.Rmd
Minor formatting edits

# Effects of species life history and data availability on integrate population model performance

@@

Code provided for peer review and may change

@@

#### compute_time_calc.R
Code for approximating the total run time, given number of simulated datasets, number of parameter scenarios, computer cores, and estimated run time for each model.

#### generate_scenarios.R

@@

#### IPM_sim_2.0function.R

@@

#### simulateTrajectories.R

@@

#### IPMinitvalues.R
Functions for putting data in the form required by the survival model.

#### IPM_marray.R
Script contains 4 IPM NIMBLE models.

@@

#### run_scenarios_helperFns.R

@@

#### run_scenarios.R

@@

#### 01_load_and_process_data.R

@@

#### 02_compute_geom_means.R

>>>>

## Effects of species life history and data availability on integrate population model performance

@@

Code provided for peer review

@@

##### compute_time_calc.R
Code for approximating the total run time, given number of simulated datasets, number of parameter scenarios, computer cores, and estimated run time for each model.

##### generate_scenarios.R

@@

##### IPM_sim_2.0function.R

@@

##### simulateTrajectories.R

@@

##### IPMinitvalues.R
Functions for putting data in the form required by the survival model.

##### IPM_marray.R
Script contains 4 IPM NIMBLE models.

@@

##### run_scenarios_helperFns.R

@@

##### run_scenarios.R

@@

##### 01_load_and_process_data.R

@@

##### 02_compute_geom_means.R
